Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-19 chi2012.tex
Finish task preparation fixed

% why? why were these tasks selected? can we drop in the phrase ``multi-dimensional subjective choice task'' and refer back to PS.1 to justify the choice of tasks?
We based our two tasks on choosing a university and picking a restaurant for a large social event, because in PS.1 the majority of people stated that they had used multiple websites for these tasks.  We used different two different variables for both tasks, where the restaurant was located (Glasgow and Cambridge) and which subject people chose (sport science and history).  The cities Glasgow and Cambridge were chosen because they are not geographically close to the participants, they are two heavily populated areas that have a choice of restaurants, and they contained detail data about the same restaurants on various review sites.  When deciding on which cities to use, we found that different areas favoured different review websites and places such as Hull had sets of disjoint sets of restaurant reviews.  We selected the top restaurants for on Tripadvisor and Yelp, because they were the top two websites people quoted for comparing reviews when travelling.  We selected the two university courses at random from a list taken form the complete university guide\footnote{The Complete University Guide:\\\url{www.thecompleteuniversityguide.co.uk}}, and selected the top six university for that subject because they provide a realistic shortlist and are comparable in terms of rankings and properties.   We selected a shortlist of six because it is typical for users to narrow down their options to a limited selection before analysing the details of their final choice.

>>>>

We based our two tasks on choosing a university and picking a restaurant for a large social event, because in PS.1 the majority of people stated that they had used multiple websites for these tasks. We used different two different variables for both tasks, where the restaurant was located (Glasgow and Cambridge) and which subject people chose (sport science and history). For the restaurant task, we chose the top restaurants in Glasgow and Cambridge from Tripadvisor and Yelp as the candidates. We chose these cities because they are not geographically close to the participants, to minimise bias). For the university condition we selected two university courses at random, and selected the top six universities for each subject. We selected a shortlist of six because it is typical for users to narrow down their options because analysing the final details of their choice.
